\section{Preliminary Problem Statement}
One of the essentials for a good \acrfull{vr} experience is a powerful computer system to render semi-realistic
worlds. However, there are two problems here. First, this type of system is not available in every location.
If realistic images have to be rendered in the simulation, it requires specialized and expensive machines that are difficult to move. 

The second problem is that for rendering the \acrshort{vr} training scenario, all kinds of data about the scenarios need to be available on the system. 
This can pose a problem when it concerns sensitive information, for example about all kinds of information defence systems or business sensitive information.


The hypothesis is that both of these problems can be resolved by a cloud rendering solution. By separating the rendering and displaying locations, \acrshort{vr} systems become much more versatile. For example with only a lightweight client necessary these experiences could be offered as a Pay-What-You-Use service, which would make them more accessible to a broader audience. Furthermore security would be improved since sensitive data never leaves the secure server location.


The aim of this report is to investigate the feasibility of a streaming based \acrshort{vr} approach, with emphasis on Latency reduction and Security.
Qualitative research methods will be used to gain in-depth insights about existing solutions and the current state of research into this topic.
The data will be contextualized via a literature review of recent research papers and capabilities of existing solutions when applied to the research problem.